\normalsize{A general approach and tool to evaluate the effectiveness of no-take marine reserves}

### 2017-08-17 Manuscript.Rmd
Updated legend of socrecard

![Scorecard for the "La Plana / Las Cuevas" marine reserve in Isla Natividad, Mexico. This scorecard was produced by MAREA.)](./Figures/scorecard.png){ width=50% }

>>>>

![Scorecard produced by MAREA for the "La Plana / Las Cuevas" marine reserve in Isla Natividad, Mexico.](./Figures/scorecard.png){ width=50% }
